02-preliminary-analysis

### 2024-06-03 data/01-census-and-traveltimes.qmd
Draft using SOM method

                                      "v_CA21_7647", # % total - walked to work
                                      "v_CA21_7635", # % total - drove or was driven to work
                                      "v_CA21_7644", # % total - used transit to get to work
                                      "v_CA21_7650", # % total - biked to work
                                      "v_CA21_7653" # % total - used some other mode to get to work
                                      ), 
                                      level='DA', use_cache = FALSE, geo_format = 'sf', quiet = TRUE)

>>>>

                                      "v_CA21_7647", # % total - walked to work
                                      "v_CA21_7635", # % total - drove or was driven to work
                                      "v_CA21_7644", # % total - used transit to get to work
                                      "v_CA21_7650", # % total - biked to work
                                      "v_CA21_7653", # % total - used some other mode to get to work

                                      "v_CA21_4306", # % of owner households with a mortgage,
                                      "v_CA21_4307", # % of owner households spending 30% or more of its income on shelter costs,
                                      "v_CA21_4308", # % of owner households in core housing need
                                      "v_CA21_4314", # % of tenant households in subsidized housing
                                      "v_CA21_4315", # % of tenant households spending 30% or more of its income on shelter costs,
                                      "v_CA21_4316" # % in core housing need

                                      ), 
                                      level='DA', use_cache = FALSE, geo_format = 'sf', quiet = TRUE)

### 2024-06-03 data/02-access-and-prelim-plots.qmd
Draft using SOM method

---
title: "02-preliminary-analysis"
format: html
---
```{r}
rm(list = ls())
```

Working with the parcel to dest TTM - walk and cycling.

```{r library-setup}
library(biscale)
library(cowplot)
library(sf)
library(here)
library(dplyr)
library(tmap)
library(mapview)
library(tmaptools)
library(pander)
library(flextable)
library(ftExtra)
library(scales)
library(here)
```

@@

load("parcel-ttm/ttm_care_bike_parcel1.rda")
load("parcel-ttm/ttm_care_bike_parcel2.rda")
load("parcel-ttm/ttm_care_bike_parcel3.rda")
load("parcel-ttm/ttm_care_bike_parcel4.rda")
load("parcel-ttm/ttm_care_walk_parcel1.rda")
load("parcel-ttm/ttm_care_walk_parcel2.rda")
load("parcel-ttm/ttm_care_walk_parcel3.rda")
load("parcel-ttm/ttm_care_walk_parcel4.rda")

ttm_care_bike_parcel <-rbind(ttm_care_bike_parcel1, ttm_care_bike_parcel2,
                             ttm_care_bike_parcel3, ttm_care_bike_parcel4)
rm(ttm_care_bike_parcel1, ttm_care_bike_parcel2, ttm_care_bike_parcel3, ttm_care_bike_parcel4)

@@

ttm_care_walk_parcel <- left_join(ttm_care_walk_parcel, R_PARCELS_CENTS_GeoUIDs_IDs, by = c("from_id"="ID"))
ttm_care_bike_parcel <- left_join(ttm_care_bike_parcel, R_PARCELS_CENTS_GeoUIDs_IDs, by = c("from_id"="ID"))
```

@@

```{r}
# all Care_Category_Specific should be represented, i.e., each ID should have 14 rows -- if that category is empty it should be 0. Let's add those 0s. 
access_15_zeros <- 
  data.frame(from_id = rep(R_PARCELS_CENTS_2020$ID, length(access_15$Care_Category_Specific |> unique())),
           Care_Category = rep(c("Dependent-centric", "Dependent-centric", "Grocery-centric", "Dependent-centric", 
                                 "Dependent-centric", "Dependent-centric",
                                 "Errand-centric", "Errand-centric", 
                                 "Grocery-centric","Health-centric",
                                 "Health-centric", "Errand-centric",
                                 "Dependent-centric", "Health-centric"), length(R_PARCELS_CENTS_2020$ID)),

@@

Aggregating time!
```{r}
#ID = care destination ID (in care_dest), GeoUID is id of the DA, from_id is parcel ID
save(access_15, file= file.path(here("data/access_15.rda")), compress = "xz")
```

@@

```{r}
#by DA and mean:
access_15_DA <- access_15 |>
  left_join(HAM_census_21 |> st_drop_geometry() |> select(c("GeoUID", "Population", "Dwellings", "LICO_AT_TOTAL", "COMMUNITY_")), 
            by=c("GeoUID")) |> 
  group_by(GeoUID) |>
  summarise(copp_iscDA_med = median(copp_isc), #the median number of opportunities (all) that can be reached from each parcel in a DA
            copp_iscDA_sd = sd(copp_isc), #the SD
            V_iscDA = sum(V_isc), #the number of total spatially available opportunities (all) that can be reached from each parcel in a DA
            vv_iscDA = sum(V_isc)/first(Population), #the per-capita number of total spatially available opportunities (all) that can be reached from each parcel in a DA
            Population = first(Population),
            Dwellings = first(Dwellings),
            LICO_AT_TOTAL = first(LICO_AT_TOTAL),
            COMMUNITY_ = first(COMMUNITY_)) |>
  tidyr::drop_na(Population)

#add the number of parcels per DA 
R_PARCELS_CENTS_count_GeoUID <- R_PARCELS_CENTS_GeoUIDs_IDs |> group_by(GeoUID) |> summarise(parcel_count = n())
access_15_DA <- access_15_DA |> left_join(R_PARCELS_CENTS_count_GeoUID, by="GeoUID")
access_15_DA <- left_join(HAM_census_21 |> select(c(GeoUID)), access_15_DA, by=c("GeoUID"))

@@

#checks
# access_15_DA |> summary()
access_15_bycategory_DA |> summary()
access_15_DA$V_iscDA |> sum(na.rm=T)
access_15_bycategory_DA$V_ic |> sum(na.rm=T)
access_15_byspecificcategory_DA$V_isc |> sum(na.rm=T)

@@

all_cats <- left_join(HAM_census_21 |> select(c(GeoUID)), all_cats, by=c("GeoUID"))
```

```{r message=FALSE}
#tmap_mode("plot")
all_cats_copp_plot <- tm_shape(ham_bay, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0) +
  tm_shape(hydro_p_LakeOntario, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0)+
  tm_shape(all_cats) +
  tm_polygons("Care_Access_Status",
              border.alpha = 0.2,
              palette = c("darkred", "orangered", "orange", "yellow", "forestgreen", "lightgreen"),
              title = "Number of care destinations spatially accessible within 15 min. walk",
              legend.is.portrait = TRUE) +
  tm_shape(Community_Boundaries) + tm_polygons(alpha=0)+
  tm_scale_bar(position = c("left", "bottom"), breaks = c(0, 1, 5, 10, 15)) +
  tm_compass(position = c("right", "top"), size=1.0)+
  tm_layout(bg.color = "grey",
            panel.label.bg.color = "white",
            panel.label.color = "black",
            legend.outside = TRUE,
            legend.position = c("center", "bottom"),
            legend.outside.position = "bottom",
            legend.outside.size = 0.2,
            legend.width = 12
            # legend.title.size = 0.7,
            # legend.text.size = 0.6
            )

@@

```{r}
all_cats_entropy_copp_plot <- tm_shape(ham_bay, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0) +
  tm_shape(hydro_p_LakeOntario, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0)+
  tm_shape(all_cats) +
  tm_polygons("entropy_copp_isc",
              border.alpha = 0.2,
              palette = "Reds",
              title = "Diversity of care destinations spatially accessible within 15 min. walk",
              legend.is.portrait = TRUE) +
  tm_shape(Community_Boundaries) + tm_polygons(alpha=0)+
  tm_scale_bar(position = c("left", "bottom"), breaks = c(0, 1, 5, 10, 15)) +
  tm_compass(position = c("right", "top"), size=1.0)+
  tm_layout(bg.color = "grey",
            panel.label.bg.color = "white",
            panel.label.color = "black",
            legend.outside = TRUE,
            legend.position = c("center", "bottom"),
            legend.outside.position = "bottom",
            legend.outside.size = 0.2,
            legend.width = 12)

tmap_save(all_cats_entropy_copp_plot, file= file.path(here("figures/all_cats_entropy_copp_plot.tiff")), dpi=600)
```

```{r}
all_cats_vvi_plot <- tm_shape(ham_bay, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0) +
  tm_shape(hydro_p_LakeOntario, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0)+
  tm_shape(all_cats) +
  tm_polygons("vvi",
              border.alpha = 0.2,
              palette = c("orangered", "forestgreen"),
              breaks = c(0, 0.003804, 0.022174),
              labels = c("Below Median", "Median and above"),
              title = "Per capita spatially available care destinations within 15 min. walk",
              legend.is.portrait = TRUE) +
  tm_shape(Community_Boundaries) + tm_polygons(alpha=0)+
  tm_scale_bar(position = c("left", "bottom"), breaks = c(0, 1, 5, 10, 15)) +
  tm_compass(position = c("right", "top"), size=1.0)+
  tm_layout(bg.color = "grey",
            panel.label.bg.color = "white",
            panel.label.color = "black",
            legend.outside = TRUE,
            legend.position = c("center", "bottom"),
            legend.outside.position = "bottom",
            legend.outside.size = 0.2,
            legend.width = 12
            )

@@

```{r}
all_cats_bivariate_entropy_copp_plot <- tm_shape(ham_bay, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0) +
  tm_shape(hydro_p_LakeOntario, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0)+
  tm_shape(all_cats) +
  tm_polygons("bivariate_entropy",
              border.alpha = 0.2,
              palette = c("yellowgreen","yellow","blue", "#FFFFDF"),
              title = "Diversity of care destinations spatially accessible within 15 min. walk",
              legend.is.portrait = TRUE) +
  tm_shape(Community_Boundaries) + tm_polygons(alpha=0)+
  tm_scale_bar(position = c("left", "bottom"), breaks = c(0, 1, 5, 10, 15)) +
  tm_compass(position = c("right", "top"), size=1.0)+
  tm_layout(bg.color = "grey",
            panel.label.bg.color = "white",
            panel.label.color = "black",
            legend.outside = TRUE,
            legend.position = c("center", "bottom"),
            legend.outside.position = "bottom",
            legend.outside.size = 0.2,
            legend.width = 12)

tmap_save(all_cats_bivariate_entropy_copp_plot, 
          file= file.path(here("figures/all_cats_bivariate_entropy_copp_plot.tiff")),
          dpi=600)
```

```{r}
care_categories_plot <- 
 tm_shape(ham_bay, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0) +
  tm_shape(hydro_p_LakeOntario, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0)+
  tm_shape(hydro_p_LakeOntario, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0)+
  tm_shape(Community_Boundaries, bbox=Community_Boundaries) + tm_polygons(col = "white", border.col = "black", lwd=1)+
  tm_shape(care_dest) + tm_dots("Care_Category_Specific", palette = RColorBrewer::brewer.pal(n = 4, name = 'Dark2'), size=0.025, title = "")+
  tm_facets("Care_Category", nrow = 2, free.scales= TRUE)+
  tm_scale_bar(position = c("left", "bottom"), breaks = c(0, 1, 5, 10, 20)) +
  tm_compass(position = c("left", "top"), size=0.9) +
  tm_layout(bg.color = "grey", panel.label.bg.color = "white", legend.position = c("right", "top"), legend.text.size = 0.5, legend.bg.color = "white", legend.bg.alpha = 0.4,
            panel.labels = c("1,265 Dependent-centric destinations", 
                             "158 Errand-centric destinations", 
                             "381 Grocery-centric destinations", 
                             "421 Health-centric destinations"),
            panel.label.size = 0.8)

tmap_save(care_categories_plot, 
          file= file.path(here("figures/care_categories_plot.tiff")),
          dpi=600)
```
```{r}
parcels_DA_plot <- 
 tm_shape(ham_bay, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0) +
  tm_shape(hydro_p_LakeOntario, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0)+
  tm_shape(access_15_DA) +
  tm_polygons("parcel_count",
              border.alpha = 0.2,
              palette = "Reds",style = "quantile", n=4,
              title = "Count of residential parcels",
              legend.is.portrait = TRUE) +
  tm_shape(Community_Boundaries) + tm_polygons(alpha=0)+
  tm_scale_bar(position = c("left", "bottom"), breaks = c(0, 1, 5, 10, 15)) +
  tm_compass(position = c("left", "top"), size=1.0)+
   tm_layout(bg.color = "grey", panel.label.bg.color = "white", legend.position = c("right", "top"), legend.text.size = 0.5,legend.title.size = 0.7,  legend.bg.color = "white", legend.bg.alpha = 0.4)

poprate_DA_plot <- 
 tm_shape(ham_bay, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0) +
  tm_shape(hydro_p_LakeOntario, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0)+
  tm_shape(access_15_DA |> mutate(popden = Population/Dwellings)) +
  tm_polygons("popden",
              border.alpha = 0.2,
              palette = "Purples", style = "quantile", n=4,
              title = "Population per dwelling",
              legend.is.portrait = TRUE) +
  tm_shape(Community_Boundaries) + tm_polygons(alpha=0)+
  tm_scale_bar(position = c("left", "bottom"), breaks = c(0, 1, 5, 10, 15)) +
  tm_compass(position = c("left", "top"), size=1.0)+
   tm_layout(bg.color = "grey", panel.label.bg.color = "white", legend.position = c("right", "top"), legend.text.size = 0.5,legend.title.size = 0.7,  legend.bg.color = "white", legend.bg.alpha = 0.4)

LICOAT_DA_plot <- 
 tm_shape(ham_bay, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0) +
  tm_shape(hydro_p_LakeOntario, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0)+
  tm_shape(access_15_DA) +
  tm_polygons("LICO_AT_TOTAL",
              border.alpha = 0.2,
              palette = "Oranges", style = "quantile", n=4,
              title = "Prevalance of household LICO-AT",
              legend.is.portrait = TRUE) +
  tm_shape(Community_Boundaries) + tm_polygons(alpha=0)+
  tm_scale_bar(position = c("left", "bottom"), breaks = c(0, 1, 5, 10, 15)) +
  tm_compass(position = c("left", "top"), size=1.0)+
   tm_layout(bg.color = "grey", panel.label.bg.color = "white", legend.position = c("right", "top"), legend.text.size = 0.5, legend.title.size = 0.7, legend.bg.color = "white", legend.bg.alpha = 0.4)

pop_descriptive_plots <- tmap_arrange(parcels_DA_plot, poprate_DA_plot, LICOAT_DA_plot, nrow=3)

tmap_save(pop_descriptive_plots, 
          file= file.path(here("figures/pop_descriptive_plots.tiff")) , asp = 1/0.6,
          dpi=600)
```

>>>>

---
title: "02-preliminary-analysis"
format: html
---
```{r}
# rm(list = ls())
```

Working with the parcel to dest TTM - walk mode.
```{r library-setup}
library(biscale)
library(cowplot)
library(sf)
library(here)
library(dplyr)
library(tmap)
library(mapview)
library(tmaptools)
library(pander)
library(flextable)
library(ftExtra)
library(scales)
library(here)
```

@@

# load("parcel-ttm/ttm_care_bike_parcel1.rda")
# load("parcel-ttm/ttm_care_bike_parcel2.rda")
# load("parcel-ttm/ttm_care_bike_parcel3.rda")
# load("parcel-ttm/ttm_care_bike_parcel4.rda")
load("parcel-ttm/ttm_care_walk_parcel1.rda")
load("parcel-ttm/ttm_care_walk_parcel2.rda")
load("parcel-ttm/ttm_care_walk_parcel3.rda")
load("parcel-ttm/ttm_care_walk_parcel4.rda")

# ttm_care_bike_parcel <-rbind(ttm_care_bike_parcel1, ttm_care_bike_parcel2,
#                              ttm_care_bike_parcel3, ttm_care_bike_parcel4)
# rm(ttm_care_bike_parcel1, ttm_care_bike_parcel2, ttm_care_bike_parcel3, ttm_care_bike_parcel4)

@@

ttm_care_walk_parcel <- left_join(ttm_care_walk_parcel, R_PARCELS_CENTS_GeoUIDs_IDs, by = c("from_id"="ID"))
#ttm_care_bike_parcel <- left_join(ttm_care_bike_parcel, R_PARCELS_CENTS_GeoUIDs_IDs, by = c("from_id"="ID"))
```

@@

```{r, eval=FALSE}
# all Care_Category_Specific should be represented, i.e., each ID should have 14 rows -- if that category is empty it should be 0. Let's add those 0s. 
access_15_zeros <- 
  data.frame(from_id = rep(R_PARCELS_CENTS_2020$ID, length(access_15$Care_Category_Specific |> unique())),
           Care_Category = rep(c("Dependent-centric", "Dependent-centric", "Grocery-centric", "Dependent-centric", 
                                 "Dependent-centric", "Dependent-centric",
                                 "Errand-centric", "Errand-centric", 
                                 "Grocery-centric","Health-centric",
                                 "Health-centric", "Errand-centric",
                                 "Dependent-centric", "Health-centric"), length(R_PARCELS_CENTS_2020$ID)),

@@

Aggregating time!
```{r, eval=FALSE}
#ID = care destination ID (in care_dest), GeoUID is id of the DA, from_id is parcel ID
save(access_15, file= file.path(here("data/access_15.rda")), compress = "xz")
```
```{r}
load(file= file.path(here("data/access_15.rda")))
```

@@

```{r}
#by DA and mean:
access_15_DA_2 <- access_15 |>
  left_join(HAM_census_21 |> st_drop_geometry() |> select(c("GeoUID", "Population", "Dwellings", "LICO_AT_TOTAL", "COMMUNITY_")), 
            by=c("GeoUID")) |> 
  group_by(GeoUID) |>
  summarise(copp_iscDA_med = median(copp_isc), #the median number of opportunities (all) that can be reached from each parcel in a DA
            copp_iscDA_sd = sd(copp_isc), #the SD
            V_iscDA = sum(V_isc), #the number of total spatially available opportunities (all) that can be reached from each parcel in a DA
            vv_iscDA = sum(V_isc)/first(Population), #the per-capita number of total spatially available opportunities (all) that can be reached from each parcel in a DA
            Population = first(Population),
            Dwellings = first(Dwellings),
            LICO_AT_TOTAL = first(LICO_AT_TOTAL),
            COMMUNITY_ = first(COMMUNITY_)) |>
  tidyr::drop_na(Population)

#add the number of parcels per DA 
R_PARCELS_CENTS_count_GeoUID <- R_PARCELS_CENTS_GeoUIDs_IDs |> group_by(GeoUID) |> summarise(parcel_count = n())
access_15_DA_2 <- access_15_DA_2 |> left_join(R_PARCELS_CENTS_count_GeoUID, by="GeoUID")
access_15_DA_2 <- left_join(HAM_census_21 |> select(c(GeoUID)), access_15_DA_2, by=c("GeoUID"))

@@

#checks
# access_15_DA_2 |> summary()
access_15_bycategory_DA |> summary()
access_15_DA_2$V_iscDA |> sum(na.rm=T)
access_15_bycategory_DA$V_ic |> sum(na.rm=T)
access_15_byspecificcategory_DA$V_isc |> sum(na.rm=T)

@@

all_cats <- left_join(HAM_census_21 |> select(c(GeoUID)), all_cats, by=c("GeoUID"))
```
<!--
SUPERCEEDED BY THE PLOTS IN 03-CLUSTERING..qmd
```{r message=FALSE, eval=FALSE}
#tmap_mode("plot")
all_cats_copp_plot <- tm_shape(ham_bay, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0) +
  tm_shape(hydro_p_LakeOntario, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0)+
  tm_shape(all_cats) +
  tm_polygons("Care_Access_Status",
              border.alpha = 0.2,
              palette = c("darkred", "orangered", "orange", "yellow", "forestgreen", "lightgreen"),
              title = "Number of care destinations spatially accessible within 15 min. walk",
              legend.is.portrait = TRUE) +
  tm_shape(Community_Boundaries) + tm_polygons(alpha=0)+
  tm_scale_bar(position = c("left", "bottom"), breaks = c(0, 1, 5, 10, 15)) +
  tm_compass(position = c("right", "top"), size=1.0)+
  tm_layout(bg.color = "grey",
            panel.label.bg.color = "white",
            panel.label.color = "black",
            legend.outside = TRUE,
            legend.position = c("center", "bottom"),
            legend.outside.position = "bottom",
            legend.outside.size = 0.2,
            legend.width = 12
            # legend.title.size = 0.7,
            # legend.text.size = 0.6
            )

@@

```{r, eval=FALSE}
all_cats_entropy_copp_plot <- tm_shape(ham_bay, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0) +
  tm_shape(hydro_p_LakeOntario, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0)+
  tm_shape(all_cats) +
  tm_polygons("entropy_copp_isc",
              border.alpha = 0.2,
              palette = "Reds",
              title = "Diversity of care destinations spatially accessible within 15 min. walk",
              legend.is.portrait = TRUE) +
  tm_shape(Community_Boundaries) + tm_polygons(alpha=0)+
  tm_scale_bar(position = c("left", "bottom"), breaks = c(0, 1, 5, 10, 15)) +
  tm_compass(position = c("right", "top"), size=1.0)+
  tm_layout(bg.color = "grey",
            panel.label.bg.color = "white",
            panel.label.color = "black",
            legend.outside = TRUE,
            legend.position = c("center", "bottom"),
            legend.outside.position = "bottom",
            legend.outside.size = 0.2,
            legend.width = 12)

tmap_save(all_cats_entropy_copp_plot, file= file.path(here("figures/all_cats_entropy_copp_plot.tiff")), dpi=600)
```
--->

```{r, eval=FALSE}
all_cats_vvi_plot <- tm_shape(ham_bay, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0) +
  tm_shape(hydro_p_LakeOntario, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0)+
  tm_shape(all_cats) +
  tm_polygons("vvi",
              border.alpha = 0.2,
              palette = c("orangered", "forestgreen"),
              breaks = c(0, 0.003804, 0.022174),
              labels = c("Below Median", "Median and above"),
              title = "Per capita spatially available care destinations within 15 min. walk",
              legend.is.portrait = TRUE) +
  tm_shape(Community_Boundaries) + tm_polygons(alpha=0)+
  tm_scale_bar(position = c("left", "bottom"), breaks = c(0, 1, 5, 10, 15)) +
  tm_compass(position = c("right", "top"), size=1.0)+
  tm_layout(bg.color = "grey",
            panel.label.bg.color = "white",
            panel.label.color = "black",
            legend.outside = TRUE,
            legend.position = c("center", "bottom"),
            legend.outside.position = "bottom",
            legend.outside.size = 0.2,
            legend.width = 12
            )

@@

```{r, eval=FALSE}
all_cats_bivariate_entropy_copp_plot <- tm_shape(ham_bay, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0) +
  tm_shape(hydro_p_LakeOntario, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0)+
  tm_shape(all_cats) +
  tm_polygons("bivariate_entropy",
              border.alpha = 0.2,
              palette = c("yellowgreen","yellow","blue", "#FFFFDF"),
              title = "Diversity of care destinations spatially accessible within 15 min. walk",
              legend.is.portrait = TRUE) +
  tm_shape(Community_Boundaries) + tm_polygons(alpha=0)+
  tm_scale_bar(position = c("left", "bottom"), breaks = c(0, 1, 5, 10, 15)) +
  tm_compass(position = c("right", "top"), size=1.0)+
  tm_layout(bg.color = "grey",
            panel.label.bg.color = "white",
            panel.label.color = "black",
            legend.outside = TRUE,
            legend.position = c("center", "bottom"),
            legend.outside.position = "bottom",
            legend.outside.size = 0.2,
            legend.width = 12)

tmap_save(all_cats_bivariate_entropy_copp_plot, 
          file= file.path(here("figures/all_cats_bivariate_entropy_copp_plot.png")),
          dpi=300)
```

```{r, eval=FALSE}
care_categories_plot <- 
 tm_shape(ham_bay, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0) +
  tm_shape(hydro_p_LakeOntario, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0)+
  tm_shape(hydro_p_LakeOntario, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0)+
  tm_shape(Community_Boundaries, bbox=Community_Boundaries) + tm_polygons(col = "white", border.col = "black", lwd=1)+
  tm_shape(care_dest) + tm_dots("Care_Category_Specific", palette = RColorBrewer::brewer.pal(n = 4, name = 'Dark2'), size=0.025, title = "")+
  tm_facets("Care_Category", nrow = 2, free.scales= TRUE)+
  tm_scale_bar(position = c("left", "bottom"), breaks = c(0, 1, 5, 10, 20)) +
  tm_compass(position = c("left", "top"), size=0.9) +
  tm_layout(bg.color = "grey", panel.label.bg.color = "white", legend.position = c("right", "top"), legend.text.size = 0.5, legend.bg.color = "white", legend.bg.alpha = 0.4,
            panel.labels = c("1,265 Dependent-centric destinations", 
                             "158 Errand-centric destinations", 
                             "381 Grocery-centric destinations", 
                             "421 Health-centric destinations"),
            panel.label.size = 0.8)

tmap_save(care_categories_plot, 
          file= file.path(here("figures/care_categories_plot.png")),
          dpi=300)
```

```{r}
## SUPERCEDED

# parcels_DA_plot <- 
#  tm_shape(ham_bay, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0) +
#   tm_shape(hydro_p_LakeOntario, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0)+
#   tm_shape(access_15_DA_2) +
#   tm_polygons("parcel_count",
#               border.alpha = 0.2,
#               palette = "Reds",style = "quantile", n=4,
#               title = "Count of residential parcels",
#               legend.is.portrait = TRUE) +
#   tm_shape(Community_Boundaries) + tm_polygons(alpha=0)+
#   tm_scale_bar(position = c("left", "bottom"), breaks = c(0, 1, 5, 10, 15)) +
#   tm_compass(position = c("left", "top"), size=1.0)+
#    tm_layout(bg.color = "grey", panel.label.bg.color = "white", legend.position = c("right", "top"), legend.text.size = 0.5,legend.title.size = 0.7,  legend.bg.color = "white", legend.bg.alpha = 0.4)
# 
# poprate_DA_plot <- 
#  tm_shape(ham_bay, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0) +
#   tm_shape(hydro_p_LakeOntario, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0)+
#   tm_shape(access_15_DA_2 |> mutate(popden = Population/Dwellings)) +
#   tm_polygons("popden",
#               border.alpha = 0.2,
#               palette = "Purples", style = "quantile", n=4,
#               title = "Population per dwelling",
#               legend.is.portrait = TRUE) +
#   tm_shape(Community_Boundaries) + tm_polygons(alpha=0)+
#   tm_scale_bar(position = c("left", "bottom"), breaks = c(0, 1, 5, 10, 15)) +
#   tm_compass(position = c("left", "top"), size=1.0)+
#    tm_layout(bg.color = "grey", panel.label.bg.color = "white", legend.position = c("right", "top"), legend.text.size = 0.5,legend.title.size = 0.7,  legend.bg.color = "white", legend.bg.alpha = 0.4)
# 
# LICOAT_DA_plot <- 
#  tm_shape(ham_bay, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0) +
#   tm_shape(hydro_p_LakeOntario, bbox=Community_Boundaries) + tm_polygons(col="skyblue", border.alpha = 0)+
#   tm_shape(access_15_DA_2) +
#   tm_polygons("LICO_AT_TOTAL",
#               border.alpha = 0.2,
#               palette = "Oranges", style = "quantile", n=4,
#               title = "Prevalance of household LICO-AT",
#               legend.is.portrait = TRUE) +
#   tm_shape(Community_Boundaries) + tm_polygons(alpha=0)+
#   tm_scale_bar(position = c("left", "bottom"), breaks = c(0, 1, 5, 10, 15)) +
#   tm_compass(position = c("left", "top"), size=1.0)+
#    tm_layout(bg.color = "grey", panel.label.bg.color = "white", legend.position = c("right", "top"), legend.text.size = 0.5, legend.title.size = 0.7, legend.bg.color = "white", legend.bg.alpha = 0.4)
# 
# pop_descriptive_plots <- tmap_arrange(parcels_DA_plot, poprate_DA_plot, nrow=2)
# 
# tmap_save(pop_descriptive_plots, 
#           file= file.path(here("figures/pop_descriptive_plots.tiff")) , asp = 1/0.6,
#           dpi=600)
```
